Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-19 providence/sections/intro.tex
Update intro.tex

We present an example to illustrate the above idea. Consider the 2020 US President contest in the state of Texas \cite{MIT-Data-Lab}; candidate Trump won with a total of 5,890,347 votes, and the second highest vote count was that of candidate Biden, who received 5,259,126 votes, for a margin of 0.056614 in the pairwise contest (that is, ignoring the votes received by other candidates). The total number of votes cast in this contest, including invalid votes and votes for other candidates (all termed {\em irrelevant} votes for this pairwise contest), was 11, 315,056. A first round size of 2,217 corresponds to a stopping probability of 0.9 and a risk limit of 0.1 for \Providence (see \cite{usenix_minerva} for a description of how first round size may be computed, \Minerva and \Providence are identical in the first round). The stopping condition of \Providence (see section \ref{sec:prov}) is a comparison of the \Providence ratio with the risk limit, stopping when the ratio is smaller. We ran two simulations using these parameters.

Assuming the tally is correct, the probability that the audit stops in the first round is 0.9. Our simulation resulted in 1,138 votes for Trump, 1,054 for Biden and the rest were irrelevant votes. The \Providence ratio for this sample is 0.047, which is smaller than the desired risk limit, 0.1 and the audit stops.

Assuming the null, a tied election, the probability that the audit stops over all possible rounds is 0.1, the risk limit. Our simulation of a five-round audit did not stop. 
%The design of the \Providence audit (see section \ref{sec:prov}) ensures that the risk of the first round is no more than 0.9 times the risk limit, and the risk expended in the first round is roughly 0.09. 
Table \ref{tab:toy} lists the round sizes, votes for both candidates and the \Providence ratio after each draw.

>>>>

We present an example to illustrate the above idea. Consider the 2020 US President contest in the state of Texas \cite{MIT-Data-Lab}; candidate Trump won with a total of 5,890,347 votes, and the second highest vote count was that of candidate Biden, who received 5,259,126 votes, for a margin of 0.056614 in the pairwise contest (that is, ignoring the votes received by other candidates). The total number of votes cast in this contest, including invalid votes and votes for other candidates (all termed {\em irrelevant} votes for this pairwise contest), was 11, 315,056. A first round size of 2,217 corresponds to a stopping probability of 0.9 and a risk limit of $\alpha=0.1$ for \Providence (see \cite{usenix_minerva} for a description of how first round size may be computed, \Minerva and \Providence are identical in the first round). The audit stops when its p-value is smaller than $\alpha$. We ran two simulations using these parameters.

The first simulation assumed the tally is correct and resulted in 1,138 votes for Trump, 1,054 for Biden (the rest were irrelevant votes). The p-value was $0.047 < \alpha$ and the audit stops.

The second simulation assumed a tied election and did not stop over five rounds. 
%The design of the \Providence audit (see section \ref{sec:prov}) ensures that the risk of the first round is no more than 0.9 times the risk limit, and the risk expended in the first round is roughly 0.09. 
Table \ref{tab:toy} lists the round sizes, votes for both candidates and the \Providence ratio after each draw.
